---
title: "R Notebook"
output: html_notebook
---

# CHapter 13

```{r}
library(sloop)
```

- S3 classes have generics, method dispatch, methods.


"The generic is a middleman: its job is to define the interface (i.e. the arguments) then find the right implementation for the job. The implementation for a specific class is called a method, and the generic finds that method by performing method dispatch."
```{r}
ftype(print)

a <- factor("a", "b", "c")
print(a) # the job of generic is to find the right method -> print.factor
print.factor(a) #calling the method directly is discouraged
```

"Generally, you can identify a method by the presence of . in the function name, but there are a number of important functions in base R that were written before S3, and hence use . to join words."

Exercises

Describe the difference between t.test() and t.data.frame(). When is each function called?

```{r}
ftype(t.test)
ftype(t.data.frame)

```
- t.test is not a method but a standard function that uses generic to find the right method for its input. Its probably an older function and thereforen named inconsistently with the above given rule.
t.data.frame is the method which generic finds when calling t() on a data.frame.

Make a list of commonly used base R functions that contain . in their name but are not S3 methods.
```{r}
ftype(is.numeric)
ftype(is.call)
# and a whole lot of other is. ...
ftype(as.array)
# as. ... is actually a S3, but not a method but generic. (array is not the method for as).
```

What does the as.data.frame.data.frame() method do? Why is it confusing? How could you avoid this confusion in your own code?

```{r}
ftype(as.data.frame.data.frame)
```
- Its a method that casts as data.frame when input is data.frame. Its called by generic as.data.frame. Maybe one could have name it differently; as_data_frame.data.frame for example.


Describe the difference in behaviour in these two calls.

```{r}
set.seed(1014)
some_days <- as.Date("2017-01-31") + sample(10, 5)

mean(some_days)
#> [1] "2017-02-06"
mean(unclass(some_days))
#> [1] 17203
```
- some_days holds 5 different dates. Mean in the first call uses generic to find date as correct method; unclass turns the dates into numerics. Probably underneath the date S3 class has a 0 for some arbitrary starting day such as 1-1-1970 and counts upwards.

What class of object does the following code return? What base type is it built on? What attributes does it use?
```{r}
x <- ecdf(rpois(100, 10))
x
#> Empirical CDF 
#> Call: ecdf(rpois(100, 10))
#>  x[1:18] =  2,  3,  4,  ..., 2e+01, 2e+01
ftype(x)
str(x)
```
- Its built from base type function. Attributes are class, as well as the call from which the function was created (ecdf is a function factory). Class are ecdf and stepfun in addition to function.

What class of object does the following code return? What base type is it built on? What attributes does it use?
```{r}
x <- table(rpois(100, 5))
x
#> 
#>  1  2  3  4  5  6  7  8  9 10 
#>  7  5 18 14 15 15 14  4  5  3
ftype(x)
str(x)
typeof(x)
class(x)
```

- A "table" class built from "integer" type.  Attributes are dimnames.

"To avoid foot-bullet intersections when creating your own class, I recommend that you usually provide three functions:

    A low-level constructor, new_myclass(), that efficiently creates new objects with the correct structure.

    A validator, validate_myclass(), that performs more computationally expensive checks to ensure that the object has correct values.

    A user-friendly helper, myclass(), that provides a convenient way for others to create objects of your class.

You don’t need a validator for very simple classes, and you can skip the helper if the class is for internal use only, but you should always provide a constructor."




## Exercises
Write a constructor for data.frame objects. What base type is a data frame built on? What attributes does it use? What are the restrictions placed on the individual elements? What about the names?

```{r}
x <- c(0,1,2)
x <- as.data.frame(x)
str(x)
typeof(x)
str(unclass(x))
```
- built from list. Each list entry is named and a vector, with attribute row.names.

```{r}
new_data_frame <- function(x, row.names) {
  stopifnot(is.list(x))
  stopifnot(!is.null(row.names))
  attr(x, "row.names") <- row.names

  x <- structure(x,
            class = "data.frame")
  
}

out <- new_data_frame(list(a = c(1,2,12)),
               row.names = c(1L,2L,3L))
```


Enhance my factor() helper to have better behaviour when one or more values is not found in levels. What does base::factor() do in this situation?

```{r}
# original
new_factor <- function(x = integer(), levels = character()) {
  stopifnot(is.integer(x))
  stopifnot(is.character(levels))

  structure(
    x,
    levels = levels,
    class = "factor"
  )
}

validate_factor <- function(x) {
  values <- unclass(x)
  levels <- attr(x, "levels")

  if (!all(!is.na(values) & values > 0)) {
    stop(
      "All `x` values must be non-missing and greater than zero",
      call. = FALSE
    )
  }

  if (length(levels) < max(values)) {
    stop(
      "There must be at least as many `levels` as possible values in `x`",
      call. = FALSE
    )
  }

  x
}

factor <- function(x = character(), levels = unique(x)) {
  ind <- match(x, levels)
  validate_factor(new_factor(ind, levels))
}




# what happens with levels not found in data in base?
x <- factor(c("a", "b"), levels = c("a", "b", "c"))
#empty level, no warning.

# for reverse case
x <- base::factor(c("a", "b", "c"), levels = c("a", "b"))
#with too few levels, without any warning!

# try with hadley
factor(c("a", "b"), levels = c("a", "b", "c"))
# already works fine

# now, levels without labels
factor(c("a", "b", "c"), levels = c("a", "b"))
# cryptic error message

# new
factor <- function(x = character(), levels = unique(x)) {
  # if (levels < unique(x) {
  #   levels <- "<NA>"
  # }
  
  ind <- match(x, levels)
  if(any(is.na(ind))) {
    levels = c(levels, "NA")
    ind[is.na(ind)] <- as.integer(max(ind, na.rm = TRUE)+1)
    warning("One or more value does not have a matching level.", call. = FALSE)
  }
  
  
  validate_factor(new_factor(ind, levels))
}

factor(c("a", "b", "c"), levels = c("a", "b"))

```

- Solution is clunky but gets the job done.


Carefully read the source code of factor(). What does it do that my constructor does not?
- ordered, labels, exclude, nmax, ifany.

Factors have an optional “contrasts” attribute. Read the help for C(), and briefly describe the purpose of the attribute. What type should it have? Rewrite the new_factor() constructor to include this attribute.

```{r}
# reset contrasts to defaults
options(contrasts = c("contr.treatment", "contr.poly"))
tens <- with(warpbreaks, C(tension, poly, 1))
attributes(tens)
## tension SHOULD be an ordered factor, but as it is not we can use
aov(breaks ~ wool + tens + tension, data = warpbreaks)

str(tens)
```
- helpful for contrast analyses in AOVs such as ANOVAs.
- contrasts is an attribute with double type, num matrix, that in turn has dimnames (a list attribute wth two sets of character vectors).
- I wont build the helper, but the constructor is in factor.R.

Read the documentation for utils::as.roman(). How would you write a constructor for this class? Does it need a validator? What might a helper do?

```{r}
r1 <- as.roman(12)
r1 + 3
str(r1)
str(unclass(r1))
```

- Takes integer and turns it into roman numeral. It remains the type integer under the hood, but the class "roman" methods convert to roman numerals.
- the constructor would be quite simple, as it only takes an integer. A validator is not necessary apart from that (with the exception of maybe 0, which is not represented in Roman), as the roman numeral is not stored in the object itself but the transformation happens in the methods.
- a helper converts the number to an integer and returns informative errors when input is numeric with decimal points etc.



## Generics and methods

Read the source code for t() and t.test() and confirm that t.test() is an S3 generic and not an S3 method. What happens if you create an object with class test and call t() with it? Why?

```{r}
x <- structure(1:10, class = "test")
t(x)
s3_dispatch(t(x))
s3_methods_generic("t")
```

- t.test is a generic (uses UseMethod) for method dispatch; its improperly named (its not a method for class "test" of generic "t"). Calling test class with t uses default. 

What generics does the table class have methods for?
What generics does the ecdf class have methods for?
Which base generic has the greatest number of defined methods?
```{r}
s3_methods_class("table")
s3_methods_class("ecdf")
s3_methods_class("numeric")
s3_methods_class("integer")
s3_methods_class("double")
s3_methods_class("Date")
s3_methods_class("data.frame")
s3_methods_class("list")
s3_methods_class("factor")

```

- It seems data.frame has a lot, followed by Date.

Carefully read the documentation for UseMethod() and explain why the following code returns the results that it does. What two usual rules of function evaluation does UseMethod() violate?

```{r}
g <- function(x) {
  x <- 10
  y <- 10
  UseMethod("g")
}
g.default <- function(x) c(x = x, y = y)

x <- 1
y <- 1
g(x)
#>  x  y 
#>  1 10
```
- g(x) uses the supplied x, but the internal x <- 10 is not used. This may be because g.default receives the x not from the environment from which it was called (g) but from the argument passed onto it. Because g.default does not accept the y argument it uses the y from its calling environment.
It therefore violates the rule that a function call recieves its argument from its calling environment, directly going to the environemnt "in which the generic function (itself) is called".
What other rule does it violate? I dont know.

From the docs:
To support this, UseMethod and NextMethod search for methods in two places: in the environment in which the generic function is called, and in the registration data base for the environment in which the generic is defined (typically a namespace). So methods for a generic function need to be available in the environment of the call to the generic, or they must be registered. (It does not matter whether they are visible in the environment in which the generic is defined.) As from R 3.5.0, the registration data base is searched after the top level environment (see topenv) of the calling environment (but before the parents of the top level environment).

6. What are the arguments to [? Why is this a hard question to answer?
```{r}
?`[`

x <- c(1,2)
`[`(x, 1)
```
- One usually does not call [] in a normal function way. The argument "x/object" is usually not passed in the classic way but written before thebracket. 

```{r}
x <- data.frame(x = 1:100, y = 1:100)
length(x)
#> [1] 2
nrow(x)
#> [1] 100
str(unclass(x))
```
### Object Styles

Categorise the objects returned by lm(), factor(), table(), as.Date(), as.POSIXct() ecdf(), ordered(), I() into the styles described above.

```{r}
x <- factor(c("a", "b", "a", "b", "c"))
length(x)
length(unclass(x))

x <- table(factor(c("a", "b", "a", "b", "c")))
length(x)
length(unclass(x))

x <- as.Date(c("2020-03-01", "2021-04-02"))
length(x)
length(unclass(x))

x <- ecdf(c(1,2,3,5,6,7,7,8,88,1,9))
length(x)
length(unclass(x))

x <- ordered(c("a", "b", "a", "b", "c"))
length(x)
length(unclass(x))

x <- I(ordered(c("a", "b", "a", "b", "c")))
length(x)
length(unclass(x))

```

- Vector styles (length(x) represents the number of observations in the vector.): factor, as.Date (Dates seem to count from unix first date as 0 upwards, just a num), ordered
- Report styles (list of equal-length vectors to represent individual components of the object):
- Scalar styles (typically use a list to represent a single thing. For example, an lm object is a list of length 12 but it represents one model.): lm, ecdf?, arguably table (a table is a single thing).

= I cannot be interpreted, instead indicating that something should be used "as is". Useful in doing things in formulas. 

What would a constructor function for lm objects, new_lm(), look like? Use ?lm and experimentation to figure out the required fields and their types.

The constructor would create an object that has the class "lm" with 12 necessary arguments. The implicit class is a list with a variety of data types in its list entries. Some of the list entries can be NULL. 

## Inheritance

Before we continue we need a bit of vocabulary to describe the relationship between the classes that appear together in a class vector. We’ll say that ordered is a subclass of factor because it always appears before it in the class vector, and, conversely, we’ll say factor is a superclass of ordered.

(Note: much more flexible than inheritance in true OOP languages like Python).

How does [.Date support subclasses? How does it fail to support subclasses?

```{r}
`[.Date`
`.Date`

x <- as.Date(c("1970-01-14", "1970-01-17"))
attr(x,  "superimportant") <- "adrenochrome" 
str(unclass(x))

x[1]
str(unclass(x[1]))
```
- calls nextMethod and then, on its output, provides the original class as argument to restore the class. This is similar to  vctrs::vec_restore(). Attributes will be dropped however it seems and therefore subclass implementation is limited.

R has two classes for representing date time data, POSIXct and POSIXlt, which both inherit from POSIXt. Which generics have different behaviours for the two classes? Which generics share the same behaviour?

```{r}
s3_methods_class("POSIXct")
s3_methods_class("POSIXlt")
s3_methods_class("POSIXt")
```
- For example, `[` are unique to the subclasses, whereas as.character, addition and subtraction is handled by the superclasses methods.

What do you expect this code to return? What does it actually return? Why?

```{r}
generic2 <- function(x) UseMethod("generic2")
generic2.a1 <- function(x) "a1"
generic2.a2 <- function(x) "a2"
generic2.b <- function(x) {
  class(x) <- "a1"
  NextMethod()
}

generic2(structure(list(), class = c("b", "a2")))
s3_dispatch(generic2(structure(list(), class = c("b", "a2"))))
```
Because method for b changes class to "a1" one would expect "a1" to be called, but "a2" is called. because nextmethod is called without arguments, it probably takes the unmodified x from the env from which function usemethod was called.

from the docs: "NextMethod invokes the next method (determined by the class vector, either of the object supplied to the generic, or of the first argument to the function containing NextMethod if a method was invoked directly). Normally NextMethod is used with only one argument, generic, but if further arguments are supplied these modify the call to the next method."

