---
title: "R Notebook"
output: html_notebook
---

 Exercises

Brainstorm as many ways as possible to extract the third value from the cyl variable in the mtcars dataset.

```{r}
mtcars$cyl[3]
mtcars[["cyl"]][[3]]
mtcars["cyl"][3,]
mtcars[3,2]
```


Given a linear model, e.g., mod <- lm(mpg ~ wt, data = mtcars), extract the residual degrees of freedom. Then extract the R squared from the model summary (summary(mod))

```{r}
mod <- lm(mpg ~ wt, data = mtcars)
mod$df.residual
summary(mod)
#str(summary(mod))
tmp <- summary(mod)
tmp$r.squared
```


    How would you randomly permute the columns of a data frame? (This is an important technique in random forests.) Can you simultaneously permute the rows and columns in one step?

    How would you select a random sample of m rows from a data frame? What if the sample had to be contiguous (i.e., with an initial row, a final row, and every row in between)?

    How could you put the columns in a data frame in alphabetical order?


```{r}
mtcars2 <- mtcars[sample(nrow(mtcars)), sample(names(mtcars))]

mtcars3 <- mtcars[sample(nrow(mtcars), 5),]
# contiguous
samplerows <- c(sample(nrow(mtcars), 1), sample(nrow(mtcars), 1)) 
samplerows <- samplerows[order(samplerows)]
mtcars3 <- mtcars[samplerows[1]:samplerows[2],]

# resort columns alphabetically 
mtcars4 <- mtcars[,colnames(mtcars)[order(colnames(mtcars))]] 
```


What type of vector does each of the following calls to ifelse() return?

```{r}
ifelse(NA, 1, "no")
str(ifelse(FALSE, 1, "no"))

x <- data.frame(x = c(1,2,3),  y = c(4,5,6))
ifelse(x, 1, "no")
ifelse(x$x == 1, 1, "no") #coerced to character

```

Thats why Hadley recommends using ifelse not with two different data types - because the coercions can produce unexpected results.


Why does this code succeed without errors or warnings?
```{r}
x <- numeric()
out <- vector("list", length(x))
for (i in 1:length(x)) {
  out[i] <- x[i] ^ 2
}
out
1:length(x)
```
Even though x is empty, the iterator is 1:0. 1:length(x) is tells it to decrease to 0. Seq_along would fixit :

```{r}
x <- numeric()
out <- vector("list", length(x))
for (i in 1:seq_along(x)) {
  out[i] <- x[i] ^ 2
}
out
1:length(x)
```
When the following code is evaluated, what can you say about the vector being iterated?
```{r}
xs <- c(1, 2, 3)
for (x in xs) {
  xs <- c(xs, x * 2)
}
xs
```
Hadley warns to use x directly rather than xs[[i]] and itearting over i, because it converts the x. In this case it will stay num thoguh. Apparently all x or the length of xs are prestored before the modification of xs, otherwise the could would return something different.

```{r}
for (i in 1:3) {
  i <- i * 2
  print(i) 
}
```

What does the following code tell you about when the index is updated?
```{r}
for (i in 1:3) {
  i <- i * 2
  print(i) 
}
#> [1] 2
#> [1] 4
#> [1] 6
```
index seems to be updated at the end of the iteration, as printing i returns the modified i value.

What does the following code return?
```{r}
x <- 10
f1 <- function(x) {
  function() {
    x + 10
  }
}
f1(1)()
```
x is looked at it in its nearest parent environment. In this case, the inner function looks at the x in the outer function, which is 1, but not at globa, where x = 10.

```{r}
`+`(1, `*`(2, 3))
```

The ticks call the function (+, -, and soon are just functions). So its the same as 
```{r}
1+(2*3)
```
```{r}
mean(, TRUE, x = c(1:10, NA))
mean(x = c(1:10,NA), ,TRUE)
```

```{r}
f2 <- function(a, b) {
  a * 10
}
f2(10, stop("This is an error!"))
```

# 9 Functionals

 9.2.6 Exercises

  Use as_mapper() to explore how purrr generates anonymous functions for the integer, character, and list helpers. What helper allows you to extract attributes? Read the documentation to find out.

```{r}
as_mapper(1)
as_mapper("string")
as_mapper(list("list"))


as_mapper(~ . + 1)

```
uses pluck when integer, cahracter or list is used as input.
when function stuff: as mapper converts input to a function using as.function, with certain specifics. Such as the ... , 

map(1:3, ~ runif(2)) is a useful pattern for generating random numbers, but map(1:3, runif(2)) is not. Why not? Can you explain why it returns the result that it does?

```{r}
map(1:3, ~ runif(2))
map(1:3, runif(2))
```
2 is not permissible as one needs to pass a function without () and pass arguments differently. It probably does not even call runif.

Use the appropriate map() function to:

Compute the standard deviation of every column in a numeric data frame.

```{r}
x <- data.frame(x = c(1,2,3), y = c(4,5,6))
map_dbl(x, sd)
```

Compute the standard deviation of every numeric column in a mixed data frame. (Hint: you’ll need to do it in two steps.)

```{r}
x <- data.frame(x = c(1,2,3), y = c(4,5,6), z = c("a", "b", "c"))

# both solutions are problematic, because they return something for non-numeric columns. best would be to first select all correct columns.
map_if(x, is.numeric, sd)
map(x, function(x) ifelse(is.numeric(x), sd(x), 0))
```


Compute the number of levels for every factor in a data frame.

```{r}
x <- data.frame(a = as.factor(c("eat", "drink", "eat", "eat")), b = as.factor(c("fuck", "shit", "up","fuck")), c = c(1,2,3,5))
map(x, levels)
map_if(x, is.factor, levels)
map_at(x, vars(is.factor), levels)
```


The following code simulates the performance of a t-test for non-normal data. Extract the p-value from each test, then visualise.

```{r}
trials <- map(1:100, ~ t.test(rpois(10, 10), rpois(7, 10)))
trials_p <- map_dbl(trials, "p.value")
hist(trials_p)
```

The following code uses a map nested inside another map to apply a function to every element of a nested list. Why does it fail, and what do you need to do to make it work?

```{r}
x <- list(
  list(1, c(3, 9)),
  list(c(3, 6), 7, c(4, 7, 6))
)

triple <- function(x) x * 3
map(x, map, .f = triple)
#> Error in .f(.x[[i]], ...): unused argument (function (.x, .f, ...)
#> {
#> .f <- as_mapper(.f, ...)
#> .Call(map_impl, environment(), ".x", ".f", "list")
#> })

# soltuion
map(x, ~ map(.x, .f = triple))
# way to write it differently? dunno
```


Use map() to fit linear models to the mtcars dataset using the formulas stored in this list:

```{r}
formulas <- list(
  mpg ~ disp,
  mpg ~ I(1 / disp),
  mpg ~ disp + wt,
  mpg ~ I(1 / disp) + wt
)

# solution
out <- map(formulas, ~lm(.x, data = mtcars))
```


Fit the model mpg ~ disp to each of the bootstrap replicates of mtcars in the list below, then extract the R2
of the model fit (Hint: you can compute the R2 with summary().)

```{r}
bootstrap <- function(df) {
  df[sample(nrow(df), replace = TRUE), , drop = FALSE]
}

bootstraps <- map(1:10, ~ bootstrap(mtcars))

# solution
fits <- map(bootstraps, ~lm(mpg ~ disp, data = .x))
map(fits, function(x) {
  tmp <- summary(x)
  tmp$r.squared
  })
```

 9.4.6 Exercises

    Explain the results of modify(mtcars, 1).
    
    ```{r}
modify(mtcars, 1)
#map(mtcars, ~length(.x))
mtcars
```

They are the same because mtcars, 1 just plucks the first column; because we enter each column at each iteration, we return the whole dataframe.

    Rewrite the following code to use iwalk() instead of walk2(). What are the advantages and disadvantages?

```{r}
cyls <- split(mtcars, mtcars$cyl)
temp <- "temp"
paths <- file.path(temp, paste0("cyl-", names(cyls), ".csv"))
walk2(cyls, paths, write.csv)
iwalk(cyls, ~write.csv(.x, file.path(temp, paste0("cyl-", .y, ".csv"))))
```
Iwalk saves a line. But walk2 is more legible.


Explain how the following code transforms a data frame using functions stored in a list.

```{r}
trans <- list(
  disp = function(x) x * 0.0163871,
  am = function(x) factor(x, labels = c("auto", "manual"))
)

nm <- names(trans)
mtcars[nm] <- map2(trans, mtcars[nm], function(f, var) f(var))
```

the .x/.y is the first function in trans and the first column in subset of mtcars[nm]; .x = f, and .y = var.
The assignment works through subassignment on the original dataframe.


Compare and contrast the map2() approach to this map() approach:
```{r}
mtcars[vars] <- map(vars, ~ trans[[.x]](mtcars[[.x]]))
```

map walks over the vars; the trans still works because the names in trans are named just like the corresponding columns.
However it is more convoluted because of the multiple [[]] subsettings/subassignments, and it wouldnt work if trans wouldnt have the correct names.

What does write.csv() return? i.e. what happens if you use it with map2() instead of walk2()?

```{r}
tmp <- map2(cyls, paths, write.csv)
```

Returns NULL, but strangely named?

